prostate

### 2023-04-05 analyses/optimOldmort.Rmd
File Changes

---
title: "dialysis"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_dialysis<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r dialysisPrep,eval=FALSE,hide=FALSE}

dialysis<-readRDS("dialysis.rds")

data <- dialysis[, c(1,2,3,4,7,6,5)]
colnames(data)[7]<-"status"

#RcmdrPlugin.survival/html/Dialysis.html

smallCenters<-as.numeric(names(which( table(data$center)<30)))
toRemove<-c()
for(i in 1:nrow(data)){
  if(data$center[i] %in% smallCenters){
    toRemove<-append(toRemove,i)
  }

}
#data<-data[-toRemove,]

preData<-data.frame(#center=as.factor(data$center),
                    age=as.numeric(data$age),
                    #begin=as.numeric(data$begin),
                    disease=as.factor(data$disease),
                    time=data$time,
                    status=data$status)

@@

saveRDS(res$test,"dialysisTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"dialysisCV.rds")

@@

klist<-readRDS("dialysisCV.rds")

@@

      ctrain<-train
      #ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")

@@

saveRDS(winners,"dialysisWins.rds")

@@

winners<-readRDS("dialysisWins.rds")

klist<-readRDS("dialysisCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("dialysisTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  source_python('src/dsurv.py')
  ctrain<-train
  ctrain$time<- train$time

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100dialysisBrier.rds')
  saveRDS(cScore,'results/100dialysiscidx.rds')
  pos=pos+1

@@

```{r plotdialysis}

BrierIPAList<-readRDS('results/100dialysisBrier.rds')

@@

cidxList<-readRDS('results/100dialysiscidx.rds')

>>>>

---
title: "oldmort"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_oldmort<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r oldmortPrep,eval=FALSE,hide=FALSE}

library(eha)

data("oldmort")

oldmort<-oldmort

omor=as.data.frame(matrix(NA,nrow=length(unique(oldmort$id)),ncol=ncol(oldmort)))
colnames(omor)<-colnames(oldmort)
unique(oldmort$id)[1]
j<-1
for(i in 1:length(unique(oldmort$id))){
  temp<-which(oldmort$id %in% unique(oldmort$id)[i])
  if(length(temp)==1){
    omor[j,]<-oldmort[temp,]
    j<-j+1
  }else if(length(temp)>1){
    tempData<-oldmort[which(oldmort$id %in% unique(oldmort$id)[i]),]
    omor[j,]<-tempData[which.min(tempData$enter),]
    omor[j,]$exit<-max(tempData$exit)
    omor[j,]$event<-sum(tempData$event)>0
    j<-j+1
  }

oldmort<-omor
preData<-data.frame(sex=as.factor(oldmort$sex),
                    civ=as.factor(oldmort$civ),
                    ses=as.factor(oldmort$ses.50),
                    birthplace=as.factor(oldmort$birthplace),
                    ageAtEntry=oldmort$enter,
                    imrAtBirth=oldmort$imr.birth,
                    region=as.factor(oldmort$region),
                    birthdate=oldmort$birthdate,
                    time=oldmort$exit-oldmort$enter,
                    status=as.numeric(oldmort$event))

@@

saveRDS(res$test,"oldmortTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"oldmortCV.rds")

@@

klist<-readRDS("oldmortCV.rds")

@@

      ctrain<-train
     ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("oldmortCV.rds")
test<-readRDS("oldmortTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("oldmortCV.rds")
test<-readRDS("oldmortTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("oldmortCV.rds")
test<-readRDS("oldmortTest.rds")

@@

saveRDS(winners,"oldmortWins.rds")

@@

winners<-readRDS("oldmortWins.rds")

klist<-readRDS("oldmortCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("oldmortTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  source_python('src/dsurv.py')
      ctrain<-train
      ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100oldmortBrier.rds')
  saveRDS(cScore,'results/100oldmortcidx.rds')
  pos=pos+1

@@

```{r plotoldmort}

BrierIPAList<-readRDS('results/100oldmortBrier.rds')

@@

cidxList<-readRDS('results/100oldmortcidx.rds')

### 2023-04-05 analyses/optimProstate.Rmd
File Changes

---
title: "flchain"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_flchain<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

reoptimize=T

@@

```{r flchainPrep,eval=FALSE,hide=FALSE}

library(survival)
flchain<-flchain

preData<-data.frame(age=as.numeric(flchain$age),
                    #sampyr=as.numeric(flchain$sample.yr),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    #batch=as.factor(flchain$flc.grp),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

@@

##saveRDS(res$test,"flchainTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
##saveRDS(klist,"flchainCV.rds")

@@

klist<-readRDS("flchainCV.rds")

# lr=c(0.001)
# drpt=c(0.25,0.5)
# layer1=c(10,20,30)
# layer2=c(10,20,30)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","linear")#,"tanh"
# alp=c(0)

@@

# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]
```

@@

##saveRDS(winners,"flchainWins.rds")

@@

winners<-readRDS("flchainWins.rds")

klist<-readRDS("flchainCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("flchainTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100flchainBrier.rds')
  saveRDS(cScore,'results/100flchaincidx.rds')
  saveRDS(AUClist,'results/100flchainAuc.rds')
  pos=pos+1

@@

```{r plotflchain}

BrierIPAList<-readRDS('results/100flchainBrier.rds')

@@

AUClist<-readRDS('results/100flchainAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100flchaincidx.rds')

>>>>

---
title: "prostate"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_prostate<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

reoptimize=F

@@

```{r prostatePrep,eval=FALSE,hide=FALSE}

library(asaur)
prostate<-prostateSurvival

prostate<-prostate[-c(which(prostate$status==2)),]

preData<-data.frame(age=as.factor(prostate$ageGroup),
                    grade=as.factor(prostate$grade),
                    stage=as.factor(prostate$stage),
                    time=as.numeric(prostate$survTime),
                    status=as.numeric(prostate$status)
)

@@

#saveRDS(res$test,"prostateTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"prostateCV.rds")

@@

klist<-readRDS("prostateCV.rds")

# 
# lr=c(0.001,0.0005)
# drpt=c(0.25,0.1)
# layer1=c(20,50,100)
# layer2=c(25,50)
# nBatch=c(100,500,1000)
# actv=c("relu","linear")#
# alp=c(0.5)

@@

#curl -d "support done" ntfy.sh/updatejykiscripts
```

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv)

#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]

@@

#saveRDS(winners,"prostateWins.rds")

@@

winners<-readRDS("prostateWins.rds")

klist<-readRDS("prostateCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("prostateTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100prostateBrier.rds')
  saveRDS(cScore,'results/100prostatecidx.rds')
  saveRDS(AUClist,'results/100prostateAuc.rds')
  pos=pos+1

@@

```{r plotprostate}

#BrierIPAList<-readRDS('results/100prostateBrier.rds')

@@

AUClist<-readRDS('results/100prostateAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100prostatecidx.rds')
